---
title: "ITF POC"
author: "yisi"
date: "July 27, 2015"
output: html_document
---

A separate function just to allow you to check whether a package is installed
```{r}
EnsurePackage <- function(packageName)
{
  x <- as.character(packageName)
  if(!require(x, character.only = TRUE))
  {
    install.packages(pkgs = x, 
                     repos = "http://cran.r-project.org")
    require(x, character.only = TRUE)
  }
} 

```

install the packages & library
```{r}
#data.table package will allow you to read files fast & delete unecessary lines & allow you to use fread(), which lets you skip lines/rows
#this is a vital package to have for this progrma particularly
EnsurePackage('data.table') 
library(data.table)

#or the following (used this one instead)
EnsurePackage('xlsx')
library('xlsx')

#following package allows you to convert table format (long to wide, and vice versa)
EnsurePackage('tidyr')
library(tidyr)

#following package is useful to use methods such as filter, summarize, etc
EnsurePackage('dplyr')
library('dplyr')

#this package will handle date & times
library('chron')

#allows u to use ddplyr
library('plyr')

```


clean up the data (for booking)
1. read the booking file which already has TAN booking
2. reorder by CBD in ascending order
3. get rid of the time clock (hour and minute)

```{r}
## 1. read file named TANed booking, which contains all the booking data for all diff TAN's (already mapped by Chenelle; couldnt map it myself b/c the files i got are already mapped)
path <- "~/cisco/LAS project w Suman/ITF/data files/"
bkRaw <- read.csv(paste(path,'arvind Order Report.csv',sep=''), header = TRUE, sep=',', check.names = TRUE)


#filter out the columns so you only keep the ones you need to use
bkRaw <- bkRaw[, c("Product.ID", "Cisco.Booked.Date", "Request.Date", "Promise.Date", "Ordered.Quantity")]

#rename the product.ID column to just PID
colnames(bkRaw)[colnames(bkRaw) == "Product.ID"] <- "PID"

#get rid of all the missing values (empty cells)
bkRaw <- bkRaw[complete.cases(bkRaw),]


```

another way to filter columns out if you know what columsn you want to drop
#get rid of sales order column; we dont need that
dropCol <- 'Sales.Order.Number'

#TAN3 = the 3rd TAN we chose to analyze
bkTAN3 <- bkTAN %>%
  filter(grepl("^800-38968", TAN)) %>%
  select(which(!(colnames(bkTAN) %in% dropCol)))
  

1. read the TAN - PID mapping and so you can map your booking data to TAN

```{r}
## 1. read file named TANed booking, which contains all the booking data for all diff TAN's (already mapped by Chenelle; couldnt map it myself b/c the files i got are already mapped)
path <- "~/cisco/LAS project w Suman/ITF/data files/"
TANtoPID <- read.csv(paste(path,'PID to TAN to PF mapping.csv',sep=''), header = TRUE, sep=',', check.names = TRUE)

#filter to read only the important columns
TANtoPID <- TANtoPID[, c("PID", "CHILD", "PF.Lead.Time")]

#the current file has TAN column name "CHILD", so get rid of the name and replace w "TAN"
colnames(TANtoPID)[colnames(TANtoPID) == "CHILD"] <- "TAN"
```


consolidate the TAN to PID mapping to the booking file
and also reorder the file
```{r}
##2. merge the two data frames (tables)
bkTAN <- merge( bkRaw, TANtoPID, by = "PID", all = TRUE)

#again, rid of empty cells
#get rid of all the missing values (empty cells)
#first convert all empty cells to NA, then use complete.cases
bkTAN[bkTAN == ''] <- NA
bkTAN <- bkTAN[complete.cases(bkTAN),]

#reorder the columns
bkTAN <- bkTAN[, c("TAN", "PID", "PF.Lead.Time", "Cisco.Booked.Date", "Request.Date", "Promise.Date", "Ordered.Quantity")]

## reorder the CBD in ascending chronological order by date and minute
#one way to reorder is to use "order" fxn and operate on dta.frame bkRaw:
#bkRaw <- bkRaw[order(as.character.Date(bkRaw$Cisco.Booked.Date), decreasing = FALSE, na.last = TRUE),]
#however, it's much faster and memory efficient to use setorder fxn on data.table bkRaw; also this set order using the reference, not a copy; so its like a hardset
bkTAN <- setorder(data.table(bkTAN), "Cisco.Booked.Date")

##  rid of clock time in CBD
bkTAN$Cisco.Booked.Date <- gsub(pattern = '[AP]M$', replacement = '', x = bkTAN$Cisco.Booked.Date)
bkTAN$Cisco.Booked.Date <- gsub(pattern = '[0-9]+:[0-9]+:[0-9]+ $', replacement = '', x = bkTAN$Cisco.Booked.Date)




```




```{r}
# #filter the data to contain only the ones that begin w 800-38968
# bkTAN3 <- subset(bkTAN, grepl("^800-38968", bkTAN$TAN))

# #now that you are left w only important columns (the ones you actually care bout); check if there's any empty spaces, and rid of those; to do so, convert all blank spaces into NA
# bkTAN3clean <- bkTAN3
# bkTAN3clean[bkTAN3clean == ''] <- NA

# #then get rid of all the NA's (since now you've already converted all blank spaces into NA, this way you can get rid of blanks and NA's at same time, if there's any NA's before you converted blanks into NA's)
# bkTAN3clean <- bkTAN3clean %>% 
#   filter(!(rowSums(is.na(bkTAN3clean)) >= 1)) 


#convert all date factors into date format, so we can do some calculation and find other important dates
#also must convert to data.frame.... otherwise won't do and IDK WHYYYYYYY QQ
bkTANwCalc <- data.frame(bkTAN)
bkTANwCalc[, grepl("Date$", colnames(bkTANwCalc))] <- as.character.Date(bkTANwCalc[, grepl(pattern = "Date$", colnames(bkTANwCalc))])


##calculation for new dates
# #initialize important key factors
# LTwk <- 4

#calculate LT goal
bkTANwCalc$LTgoal <- chron(bkTANwCalc$Cisco.Booked.Date) + bkTANwCalc$PF.Lead.Time
#the chron function will allow us to use mathematical operations such as addition and subtraction by days on the dates characters


#assign flags for whether CRD is within LT goal
bkTANwCalc$CRDinLTflag <- ifelse( chron(bkTANwCalc$Request.Date) > bkTANwCalc$LTgoal, 'outside LT', 'within LT')


#calculate current LAS hit
#so if CRD <= LT, then LAS hit (LAS = 0) when PD > LT; if CRD > LT, then LAS hit when PD > CRD
bkTANwCalc$LASnow <- ifelse( bkTANwCalc$CRDinLTflag == 'yes', ifelse( chron(bkTANwCalc$Promise.Date) > chron(bkTANwCalc$LTgoal), 0, 100), ifelse( chron(bkTANwCalc$Promise.Date) > chron(bkTANwCalc$Request.Date), 0, 100) )


```


#can use following method to check if the date is a holiday or weekend
is.weekend(x)
is.holiday(x, holidays)
is.weekend(testDate)

bkTAN3converted <- bkTAN3clean %>%
  chron(as.character(subset(bkTAN3clean, select = grepl("Date$", colnames(bkTAN3clean)))))



now work on supply file
1. read supply image 
```{r}
#1. read the supply file
path <- "~/cisco/LAS project w Suman/ITF/data files/"
suppOriginal <- read.csv(paste(path,'7-30 suman ATP SUPPLY.csv',sep=''), header = TRUE, sep=',', check.names = TRUE)

#reorganize the orders of the columns; and also select only the ones that interest you
suppReOrg <- suppOriginal[, c("TAN", "Org", "Due.Date", "Quantity", "Type")]

#since the original date formate for due date is in word and comma, e.g. June 18, 2015
#and chron doesnt read that format, first need to get rid of the comma in the date string, and then it becomes a format that chron can read; however, sitll need to convert the data type to character first (original classified as factor by R by default)
suppReOrg$Due.Date <- gsub(pattern = ',', replacement = '', x = suppReOrg$Due.Date)
suppReOrg$Due.Date <- chron(as.character(suppReOrg$Due.Date), format = 'month day year', out.format = 'm/d/y')

# 
# testsupp <- subset(suppReOrg, suppReOrg$Quantity==120)
# testsupp <- subset(suppReOrg, grepl("^800-38968", TAN))
# 
# 


```




now seperate booking & supply data by TAN into diff data frames in a list
```{r}
bkByTAN <- list()
suppByTAN <- list()

#find out the unique values of TAN and set them into a vector
TANvals <- as.character(unique(bkTAN$TAN))

for(i in 1: length(TANvals)){
  bkByTAN[[i]] <- subset(bkTAN, bkTAN$TAN == TANvals[i])
  suppByTAN[[i]] <- subset(suppReOrg, suppReOrg$TAN == TANvals[i])
}

test <- (bkByTAN[[2]])
test <- suppByTAN[[2]]

```



now lets build our model
1. set transit pad & ATP ITF pad 
2. read customer request date
is CRD <= CBD? 
  yes
    nuff supply on CBD?
      yes
      no
  no
3. aggregate all supplies before CRD
4. subtract the quantity if sufficient, then store the new available quantity

```{r}
#1. initialize transid pad to 2 days ITC
TP <- 2
ATP.ITF.pad <- 7
testbk <- bkTAN3addInfo
testsupp <- subset(suppReOrg, suppReOrg$Quantity==120)
testsupp <- subset(suppReOrg, grepl("^800-38968", TAN))

#aggregate the supply image by due.date
testsupp <- aggregate(Quantity ~ Due.Date, FUN = sum, data = testsupp)


for(i in 1:length(testbk$Request.Date)){
  print(i)
  if (chron(testbk$Request.Date[i]) <= chron(testbk$LTgoal[i])){
    #if CRD <= LT
    if ( chron(testbk$Request.Date[i]) <= chron(testbk$Cisco.Booked.Date[i]) + TP){
    #if CRD <= LT & CRD <= CBD + TP
      closestDateIndex <- which.min(abs(chron(testbk$Cisco.Booked.Date[i]) - chron(testsupp$Due.Date)))
      print(closestDateIndex)
      closestDate <- testsupp$Due.Date[closestDateIndex]
      print(closestDate)
      
      while(testbk$Ordered.Quantity[i] > 0){
        if (chron(testbk$Cisco.Booked.Date[i]) > chron(testsupp$Due.Date[closestDateIndex])){
          #if supply arrived before CBD
          if (testsupp$Quantity[closestDateIndex] >= testbk$Ordered.Quantity[i]){
            #if supply is enough
            testbk$newPD[i] <- as.character(dates(chron(testbk$Cisco.Booked.Date[i]) + TP)) 
            testsupp$Quantity[closestDateIndex] <- testsupp$Quantity[closestDateIndex] - testbk$Ordered.Quantity[i]
            testbk$Ordered.Quantity[i] <- 0
            print('CRD<=LT, CRD <= CBD, supply b4 CBD')
          } else{
            #if there's not enough supply in the nearest supply bucket
            testbk$Ordered.Quantity[i] <- testbk$Ordered.Quantity[i] - testsupp$Quantity[closestDateIndex]
            testsupp$Quantity[closestDateIndex] <- 0
            closestDateIndex <- closestDateIndex - 1
            print('CRD<=LT, CRD <= CBD, supply after CBD')
          }
        } else{
          #if supply arrived after CBD but w/in LT
          
          while(testbk$Ordered.Quantity[i] > 0){
            if (testsupp$Quantity[closestDateIndex] >= testbk$Ordered.Quantity[i]){
            #if supply is enough
            testbk$newPD[i] <- dates(testsupp$Due.Date[closestDateIndex])
            testbk$newPD[i] <- ifelse(is.weekend(testbk$newPD[i]), testbk$newPD[i] +1, testbk$newPD[i])
            testsupp$Quantity[closestDateIndex] <- testsupp$Quantity[closestDateIndex] - testbk$Ordered.Quantity[i]
            testbk$Ordered.Quantity <- 0
            print('CRD<=LT, CRD > CBD, CRD < LT, supply before CRD')
            } else{
              #if there's not enough supply in the nearest supply bucket
              testbk$Ordered.Quantity[i] <- testbk$Ordered.Quantity - testsupp$Quantity[closestDateIndex]
              testsupp$Quantity[closestDateIndex] <- 0
              closestDateIndex <- closestDateIndex + 1
              print('CRD<=LT, CRD > CBD, CRD < LT, supply after CRD')
            }
          }
        }
      }
    } else{
      
      closestDateIndex <- which.min(abs(chron(testbk$Request.Date[i]) - chron(testsupp$Due.Date)))
      print(closestDateIndex)
      closestDate <- testsupp$Due.Date[closestDateIndex]
      print(closestDate)
      
      while(testbk$Ordered.Quantity[i] > 0){
        if ((chron(testbk$Request.Date[i]) - TP) > chron(testsupp$Due.Date[closestDateIndex])){
          #if supply arrived before CRD - TP day
          if (testsupp$Quantity[closestDateIndex] >= testbk$Ordered.Quantity[i]){
            #if supply is enough TP days before Request date
            testbk$newPD[i] <- as.character(dates(chron(testbk$Request.Date[i])))
            testsupp$Quantity[closestDateIndex] <- testsupp$Quantity[closestDateIndex] - testbk$Ordered.Quantity[i]
            testbk$Ordered.Quantity[i] <- 0
            print('CRD<=LT, CRD > CBD, supply b4 CRD - TP')
          } else{
            #if there's not enough supply in the nearest supply bucket TP days before CRD
            
            if(testsupp$Due.Date[closestDateIndex] <= chron(testbk$LTgoal[i])){
              #if the supply is enough before LT
              testbk$newPD[i] <- as.character(dates(chron(testsupp$Due.Date[closestDateIndex]))) 
              testsupp$Quantity[closestDateIndex] <- testsupp$Quantity[closestDateIndex] - testbk$Ordered.Quantity[i]
              testbk$Ordered.Quantity[i] <- 0
              print('CRD<=LT, CRD > CBD, supply b4 LT after CRD')
            } else{
              #if supply is given after LT
              print('CRD<=LT, CRD > CBD, supply not enough before LT; order put on ITF + x days')
              testbk$newPD <- chron(testbk$LTgoal) + ATP.ITF.pad
              
            }
          }
        } else{
          #if supply arrived after CBD but w/in LT
          
          while(testbk$Ordered.Quantity[i] > 0){
            if (testsupp$Quantity[closestDateIndex] >= testbk$Ordered.Quantity[i]){
            #if supply is enough
            testbk$newPD[i] <- as.character(dates(testsupp$Due.Date[closestDateIndex]))  
            testsupp$Quantity[closestDateIndex] <- testsupp$Quantity[closestDateIndex] - testbk$Ordered.Quantity[i]
            testbk$Ordered.Quantity <- 0
            print('CRD<=LT, CRD > CBD, CRD < LT, supply before CRD')
            } else{
              #if there's not enough supply in the nearest supply bucket
              testbk$Ordered.Quantity[i] <- testbk$Ordered.Quantity - testsupp$Quantity[closestDateIndex]
              testsupp$Quantity[closestDateIndex] <- 0
              closestDateIndex <- closestDateIndex + 1
              print('CRD<=LT, CRD > CBD, CRD < LT, supply after CRD')
            }
          }
        }
      }
    }
  } else{
    #if CRD > LT; set PD = CRD
    testbk$newPD[i] <- testbk$Request.Date[i]
    #testbk$newPD <- testbk$Request.Date
  }
}


#calculate for the new LAS for each ship
testbk$newLAS <- ifelse( chron(testbk$Request.Date) > chron(testbk$LTgoal), 100, 
                         ifelse( chron(testbk$newPD) <= chron(testbk$LTgoal), 100, 0))













```



```{r}


```

create a table that stores all the results for all TAN's
```{r}
#create a result table (temporary like this)
#first put the TAN into the table
result <- data.table(1,2,3)
#then rename all the columns with following code
names(result) <- c("TAN", "as-is LAS", "to-be LAS")

#calculate for the as is LAS
temp <- table(bkTAN3addInfo$LAS)
asisLAS <- ifelse(is.na(temp['100']), 0, ifelse(is.na(temp['0']), 100, (temp['100'] / (temp['0'] + temp['100'])) * 100))

#need to calculate for to be LAS.... shit
temp <- table(testbk$newLAS)
tobeLAS <- ifelse(is.na(temp['100']), 0, ifelse(is.na(temp['0']), 100, (temp['100'] / (temp['0'] + temp['100'])) * 100))

#combine all 3 values
row2badd <- list(as.character(bkTAN3addInfo$TAN[1]), asisLAS, tobeLAS)

#finally modify the result table by row bind method
result <- rbind(result, row2badd)

```


```{r}


```


```{r}


```




