---
title: "ITF POC"
author: "yisi"
date: "July 27, 2015"
output: html_document
---

user input values:
please initialize all necessary constraints here
```{r}
#transit pad in days
TP <- 2
#atp itf pad in days
ATP.ITF.pad <- 7
```


A separate function just to allow you to check whether a package is installed
```{r}
EnsurePackage <- function(packageName)
{
  x <- as.character(packageName)
  if(!require(x, character.only = TRUE))
  {
    install.packages(pkgs = x, 
                     repos = "http://cran.r-project.org")
    require(x, character.only = TRUE)
  }
} 

```

install the packages & library
```{r}
#data.table package will allow you to read files fast & delete unecessary lines & allow you to use fread(), which lets you skip lines/rows
#this is a vital package to have for this progrma particularly
EnsurePackage('data.table') 
library(data.table)

#or the following (used this one instead)
EnsurePackage('xlsx')
library('xlsx')

#following package allows you to convert table format (long to wide, and vice versa)
EnsurePackage('tidyr')
library(tidyr)

#following package is useful to use methods such as filter, summarize, etc
EnsurePackage('dplyr')
library('dplyr')

#this package will handle date & times
library('chron')

#allows u to use ddplyr
library('plyr')

```


clean up the data (for booking)
1. read the booking file which already has TAN booking
2. reorder by CBD in ascending order
3. get rid of the time clock (hour and minute)

```{r}
## 1. read file named TANed booking, which contains all the booking data for all diff TAN's (already mapped by Chenelle; couldnt map it myself b/c the files i got are already mapped)
path <- "~/cisco/LAS project w Suman/ITF/data files/"
bkRawOrig <- read.csv(paste(path,'9-1 wk of 6-28 Order Report_Arvind.csv',sep=''), header = TRUE, sep=',', check.names = TRUE)

#filter out unwanted columns
colDrop <- c("Demand.Class", "Org.Code", "Last.Updated.Date")
bkRaw <- bkRawOrig[, !(names(bkRawOrig) %in% colDrop)]

# #filter out the columns so you only keep the ones you need to use
# bkRaw <- bkRaw[, c("Product.ID", "Cisco.Booked.Date", "Requested.Ship.Date", "Promise.Date", "Ordered.Quantity")]

# #rename the product.ID column to just PID
# colnames(bkRaw)[colnames(bkRaw) == "Product.ID"] <- "PID"

#get rid of all the missing values (empty cells)
bkRaw <- bkRaw[complete.cases(bkRaw),]


```

another way to filter columns out if you know what columsn you want to drop
#get rid of sales order column; we dont need that
dropCol <- 'Sales.Order.Number'

#TAN3 = the 3rd TAN we chose to analyze
bkTAN3 <- bkTAN %>%
  filter(grepl("^800-38968", TAN)) %>%
  select(which(!(colnames(bkTAN) %in% dropCol)))
  

read the TAN - PID mapping and so you can map your booking data to TAN
then map TAN to PF
then map PF to LT
so basically your final goal is to map TAN with LT
```{r}
# ## 1. read file named TANed booking, which contains all the booking data for all diff TAN's (already mapped by Chenelle; couldnt map it myself b/c the files i got are already mapped)
# path <- "~/cisco/LAS project w Suman/ITF/data files/"
# TANtoPID <- read.csv(paste(path,'8-31 Arvind_PID_TAN_Data.csv',sep=''), header = TRUE, sep=',', check.names = TRUE)
# 
# #filter to read only the important columns
# TANtoPID <- TANtoPID[, c("TOP_PID", "CHILD_ITEM")]
# 
# #the current file has TAN column name "CHILD", so get rid of the name and replace w "TAN"
# colnames(TANtoPID)[colnames(TANtoPID) == "CHILD_ITEM"] <- "TAN"

##now map TAN to PF; or PID to PF
path <- "~/cisco/LAS project w Suman/ITF/data files/"
TANtoPF <- read.csv(paste(path,'9-1 TAN-PID-PF-BU.csv',sep=''), header = TRUE, sep=',', check.names = TRUE, skip = 1)
TANtoPF <- TANtoPF[, c("PID", "TAN", "Prod.Family")]

## now map PF to LT
path <- "~/cisco/LAS project w Suman/ITF/data files/"
PFtoLT <- read.csv(paste(path,'9-1 PF-LTGoal Mapping.csv',sep=''), header = TRUE, sep=',', check.names = TRUE)
PFtoLT <- PFtoLT[, !(colnames(PFtoLT) == 'LT_wk')]

##now merge this two files first
TANPFLT <- merge(TANtoPF, PFtoLT, by = 'Prod.Family', all.x = TRUE)
#now you can use this to map with the booking file

```


consolidate the TAN to PID to PF to LT mapping to the booking file 
and also reorder the file
```{r}
##2. merge the two data frames (tables); we dont need all the TAN-PID mapping, but we do need to keep all the booking info
bkTAN <- merge( bkRaw, TANPFLT, by.x = "Product.ID", by.y = "PID", all.x = TRUE)

#store original ordered quantity; this is more for my self-checking during processes
bkTAN$orig.Ordered.Qty <- bkTAN$Ordered.Quantity

# #again, rid of empty cells
# #get rid of all the missing values (empty cells)
# #first convert all empty cells to NA, then use complete.cases
# bkTAN[bkTAN == ''] <- NA
# bkTAN <- bkTAN[complete.cases(bkTAN),]

#get rid of all the rows with promise date after 8/31, which is the day arvind got his report
#so anything with PD after this date, we dont have the actual ship date data; no use, so rid of
retrieveDate <- '8/31/2015'
bkSDvalid <- subset(bkTAN, chron(as.character(bkTAN$Promise.Date)) < chron(as.character(retrieveDate)))


# #reorder the columns
# bkTAN <- bkTAN[, c("TAN", "PID", "PF.Lead.Time", "Cisco.Booked.Date", "Requested.Ship.Date", "Promise.Date", "orig.Ordered.Qty", "Ordered.Quantity")]

bkSDclean <- bkSDvalid

#to reorder the book date data, must convert the time from 12 hour format to 24 hour format first
bkSDclean$Cisco.Booked.Date <- as.character(strptime(bkSDclean$Cisco.Booked.Date, "%m/%d/%Y %I:%M:%S %p"))
#the time format at the end must match the input time format

## reorder the CBD in ascending chronological order by date and minute
#one way to reorder is to use "order" fxn and operate on dta.frame bkRaw:
#bkRaw <- bkRaw[order(as.character.Date(bkRaw$Cisco.Booked.Date), decreasing = FALSE, na.last = TRUE),]
#however, it's much faster and memory efficient to use setorder fxn on data.table bkRaw; also this set order using the reference, not a copy; so its like a hardset
bkSDclean <- setorder(data.table(bkSDclean), "Cisco.Booked.Date")


##  rid of clock time in CBD
#bkSDclean$Cisco.Booked.Date <- gsub(pattern = '[AP]M$', replacement = '', x = bkSDclean$Cisco.Booked.Date)
bkSDclean$Cisco.Booked.Date <- gsub(pattern = '[0-9]+:[0-9]+:[0-9]+$', replacement = '', x = bkSDclean$Cisco.Booked.Date)
#also have to change the booked date format to with slash instead of with hyphen
bkSDclean$Cisco.Booked.Date <- gsub(pattern = '-', replacement = "/", x = bkSDclean$Cisco.Booked.Date)
bkSDclean$Cisco.Booked.Date <- chron(bkSDclean$Cisco.Booked.Date, format = "y/m/d", out.format = 'm/d/y')


```



calculate LAS now
calculate OTS now
```{r}
#convert all date factors into date format, so we can do some calculation and find other important dates
#also must convert to data.frame.... otherwise won't do and IDK WHYYYYYYY QQ
bkSDwCalc <- data.frame(bkSDclean)
bkSDwCalc[, grepl("Date$", colnames(bkSDwCalc))] <- as.character.Date(bkSDwCalc[, grepl(pattern = "Date$", colnames(bkSDwCalc))])

#calculate LT goal
bkSDwCalc$LTgoal <- chron(bkSDwCalc$Cisco.Booked.Date) + bkSDwCalc$LT_day
#the chron function will allow us to use mathematical operations such as addition and subtraction by days on the dates characters


#assign flags for whether CRD is within LT goal
bkSDwCalc$CRDinLTflag <- ifelse( chron(bkSDwCalc$Requested.Ship.Date) > chron(bkSDwCalc$LTgoal), 'N', 'Y')


#calculate current LAS hit
#so if CRD <= LT, then LAS hit (LAS = 0) when PD > LT; if CRD > LT, then LAS hit when PD > CRD
bkSDwCalc$LASnow <- ifelse( bkSDwCalc$CRDinLTflag == 'Y', ifelse( chron(bkSDwCalc$Original.Promise.Date) > chron(bkSDwCalc$LTgoal), 0, 100), ifelse( chron(bkSDwCalc$Original.Promise.Date) > chron(bkSDwCalc$Requested.Ship.Date), 0, 100) )

#calculate current OTS hit
bkSDwCalc$OTSnow <- ifelse( bkSDwCalc$CRDinLTflag == 'Y', ifelse( chron(bkSDwCalc$Ship.Date) > chron(bkSDwCalc$LTgoal), 0, 100), ifelse( chron(bkSDwCalc$Ship.Date) > chron(bkSDwCalc$Original.Promise.Date), 0, 100) )

```


now work on supply file
1. read supply image 
```{r}
#1. read the supply file
path <- "~/cisco/LAS project w Suman/ITF/data files/"
suppOriginal <- read.csv(paste(path,'7-30 suman ATP SUPPLY.csv',sep=''), header = TRUE, sep=',', check.names = TRUE)

#reorganize the orders of the columns; and also select only the ones that interest you
suppReOrg <- suppOriginal[, c("TAN", "Org", "Due.Date", "Quantity", "Type")]

# #since the original date formate for due date is in word and comma, e.g. June 18, 2015
# #and chron doesnt read that format, first need to get rid of the comma in the date string, and then it becomes a format that chron can read; however, sitll need to convert the data type to character first (original classified as factor by R by default)
# suppReOrg$Due.Date <- gsub(pattern = ',', replacement = '', x = suppReOrg$Due.Date)
# suppReOrg$Due.Date <- chron(as.character(suppReOrg$Due.Date), format = 'month day year', out.format = 'm/d/y')

#convert due date into a date format
suppReOrg$Due.Date <- chron(as.character(suppReOrg$Due.Date))

#convert quantity into numeric; right now its factor
suppReOrg$Quantity <- as.numeric(levels(suppReOrg$Quantity)[suppReOrg$Quantity])

#duplicate the quantity column in supply image to save the original quantity and so you can compare the values later
suppReOrg$Orig.Qty <- suppReOrg$Quantity

```




now seperate booking & supply data by TAN into diff data frames in a list
```{r}
#1. initialize the lists
bkByTAN <- list()
suppByTAN <- list()

#find out the unique values of TAN and set them into a vector
#TANvals <- as.character(unique(bkSDwCalc$TAN))
#i'll hard code TAN's for now
TANvals <- c("68-4856-01","68-4697-02", "800-38968-01", "800-38502-01", "800-38513-01")

##now comes the monster code.... where you need 2 for loops, 1 to iterate through the master list (4 tans in this case), one to iterate through all the request date in each data.frame of the list

# for(j in 1: length(TANvals)){
#   suppByTAN[[j]]$Due.Date <- as.character(chron(suppByTAN[[j]]$Due.Date))
# }

for(j in 1: length(TANvals)){
  #print(paste('j = ', j))
  #first separate all booking and supply data by TAN into diff data.frames
  bkByTAN[[j]] <- bkSDwCalc[bkSDwCalc$TAN == TANvals[j], ]
  suppByTAN[[j]] <- suppReOrg[suppReOrg$TAN == TANvals[j], ]
  
  #aggregate the supply image by due.date
  #suppByTAN[[j]] <- ddply(suppByTAN[[j]], "Due.Date", numcolwise(sum))
}

testbk <- bkByTAN[[1]]
testsup <- suppByTAN[[1]]
# names(testbk)
  
for(j in 1: length(TANvals)){
  print(paste('j = ', j))
  j<-1
  #to iterate through all individual TANs
  for(i in 1:length(bkByTAN[[j]]$Requested.Ship.Date)){
    print(paste('i = ', i))
    
    if (chron(bkByTAN[[j]]$Requested.Ship.Date[i]) <= chron(bkByTAN[[j]]$LTgoal[i]) - TP){
      #if CRD <= LT - TP
      if ( chron(bkByTAN[[j]]$Requested.Ship.Date[i]) <= chron(bkByTAN[[j]]$Cisco.Booked.Date[i]) + TP){
        print('CRD <= CBD + TP')
      #if CRD <= LT - TP & CRD <= CBD + TP
        #also gotta make sure the first bucket to check is before booked date; backward looking
        closestDateIndex <- which.min(abs(chron(bkByTAN[[j]]$Cisco.Booked.Date[i]) - suppByTAN[[j]]$Due.Date))
        closestDateIndex <- ifelse(chron(bkByTAN[[j]]$Cisco.Booked.Date[i]) < suppByTAN[[j]]$Due.Date[closestDateIndex], closestDateIndex - 1, closestDateIndex)

        closestDate <- suppByTAN[[j]]$Due.Date[closestDateIndex]
        closestDateIndexInitial <- closestDateIndex
        
      
        if (chron(bkByTAN[[j]]$Cisco.Booked.Date[i]) > suppByTAN[[j]]$Due.Date[closestDateIndex]){
          #if supply arrived before CBD
          if (suppByTAN[[j]]$Quantity[closestDateIndex] >= bkByTAN[[j]]$Ordered.Quantity[i]){
            #if supply is enough before CBD
            #then PD = CBD + TP
            bkByTAN[[j]]$newPD[i] <- as.character(chron(bkByTAN[[j]]$Cisco.Booked.Date[i]) + TP) 
            #gotta check if the new PD is on a weekend or not
            bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
            #need another one in case above one pushes the date from sat to sunday
            bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
            #also update the supply image by subtracting the ordered qty
            suppByTAN[[j]]$Quantity[closestDateIndex] <- suppByTAN[[j]]$Quantity[closestDateIndex] - bkByTAN[[j]]$Ordered.Quantity[i]
            #and then also set ordered qty to 0
            bkByTAN[[j]]$Ordered.Quantity[i] <- 0
            #OK print('CRD<=LT, CRD <= CBD + TP, supply b4 CBD')
          } else{
            #if there's not enough supply in the nearest supply bucket before CBD
            endReached <- FALSE
            #then take out the quantity from the nearest backward bucket first; to do that, subtract the available qty from the ordered qty, then set that bucket supply to 0
            
            while(bkByTAN[[j]]$Ordered.Quantity[i] > 0){
              print('while 1')
              if(bkByTAN[[j]]$Ordered.Quantity[i] <= suppByTAN[[j]]$Quantity[closestDateIndex]){
                #if there's enough supply
                if(endReached == FALSE){
                # backward looking has not reached end yet
                #OK print('backward looking has not reached end yet')
                bkByTAN[[j]]$newPD[i] <- as.character(chron(bkByTAN[[j]]$Cisco.Booked.Date[i]) + TP) 
                #again, check if new PD is on wknd
                bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) + 1), bkByTAN[[j]]$newPD[i])
                bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) + 1), bkByTAN[[j]]$newPD[i])
                #also update the supply image by subtracting the ordered qty
                suppByTAN[[j]]$Quantity[closestDateIndex] <- suppByTAN[[j]]$Quantity[closestDateIndex] - bkByTAN[[j]]$Ordered.Quantity[i]
                #and then also set ordered qty to 0
                bkByTAN[[j]]$Ordered.Quantity[i] <- 0
                
                } else{ #if endReached = TRUE
                  #backward looking has reached end 
                  bkByTAN[[j]]$newPD[i] <- as.character(suppByTAN[[j]]$Due.Date[closestDateIndex] + TP)
                  bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
                  bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
                  suppByTAN[[j]]$Quantity[closestDateIndex] <- suppByTAN[[j]]$Quantity[closestDateIndex] - bkByTAN[[j]]$Ordered.Quantity[i]
                  bkByTAN[[j]]$Ordered.Quantity[i] <- 0
                  #OK print('backward looking has reached end')
                  } #end of else for backward looking end reached
              } else{
                #if there's not enough suppply w/in this bucket
                bkByTAN[[j]]$Ordered.Quantity[i] <- bkByTAN[[j]]$Ordered.Quantity[i] - suppByTAN[[j]]$Quantity[closestDateIndex]
                suppByTAN[[j]]$Quantity[closestDateIndex] <- 0
                
                if(closestDateIndex > 0){
                  if(endReached == FALSE){
                    #then go backward even further if you still have buckets to go
                    closestDateIndex <- closestDateIndex - 1
                  } else{
                    #go forward if you've already reached end of supply bucket
                    closestDateIndex <- closestDateIndex + 1
                  }
                  #OK print('closestDateIndex is still positive')
                } else{
                  #otherwise, go forward to the next nearest bucket
                  endReached <- TRUE
                  closestDateIndex <- closestDateIndexInitial + 1
                  #OK print('closestDateIndex = 0')
                } #end of else: otherwise, go forward
              } #end of else: if there's not supply w/in this bucket
            } #end of while qty > 0 
          } #end of else: if theres not enough supply in nearest supply bucket
            
            
        } else{
          #if supply arrived after CBD but w/in LT - TP
          if (suppByTAN[[j]]$Quantity[closestDateIndex] >= bkByTAN[[j]]$Ordered.Quantity[i]){
            #if supply is enough
            bkByTAN[[j]]$newPD[i] <- as.character(suppByTAN[[j]]$Due.Date[closestDateIndex])
            bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
            bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
            suppByTAN[[j]]$Quantity[closestDateIndex] <- suppByTAN[[j]]$Quantity[closestDateIndex] - bkByTAN[[j]]$Ordered.Quantity[i]
            bkByTAN[[j]]$Ordered.Quantity[i] <- 0
            #print('CRD<=LT, CRD > CBD, CRD < LT, supply before CRD')
          } else{
          #if there's not enough supply in the nearest supply bucket
            
            while(bkByTAN[[j]]$Ordered.Quantity[i] > 0){
              print('while 2')
              bkByTAN[[j]]$Ordered.Quantity[i] <- bkByTAN[[j]]$Ordered.Quantity[i] - suppByTAN[[j]]$Quantity[closestDateIndex]
              suppByTAN[[j]]$Quantity[closestDateIndex] <- 0
              closestDateIndex <- closestDateIndex + 1
            } #end of while
            #print('CRD<=LT, CRD > CBD, CRD < LT, supply after CRD')
          } #end of else: if there's not enough supply
        } #end of else: if supply arrived after CBD but w/in LT
      }else if (chron(bkByTAN[[j]]$Requested.Ship.Date[i]) > (chron(bkByTAN[[j]]$Cisco.Booked.Date[i]) + TP)){
      #if CRD <= LT - TP & CRD > CBD + TP
        
        #update closestDateIndex to index to the supply date closest to CRD
        closestDateIndex <- which.min(abs((chron(bkByTAN[[j]]$Requested.Ship.Date[i]) - TP) - suppByTAN[[j]]$Due.Date))
        closestDateIndex <- ifelse(chron(bkByTAN[[j]]$Requested.Ship.Date[i]) < suppByTAN[[j]]$Due.Date[closestDateIndex], closestDateIndex - 1, closestDateIndex)
        #i had closestDateIndex + 1 before; now corrected (i think)
        
        closestDate <- suppByTAN[[j]]$Due.Date[closestDateIndex]
        closestDateIndexInitial <- closestDateIndex
  
        while(bkByTAN[[j]]$Ordered.Quantity[i] > 0){
          print('while 3')
          if ((chron(bkByTAN[[j]]$Requested.Ship.Date[i]) - TP) > suppByTAN[[j]]$Due.Date[closestDateIndex]){
            print('if 1')
            #if supply arrived before CRD - TP day; CRD > Due.Date
            if (suppByTAN[[j]]$Quantity[closestDateIndex] >= bkByTAN[[j]]$Ordered.Quantity[i]){
              print('if 1.1')
              #if supply is enough TP days before Request date
              bkByTAN[[j]]$newPD[i] <- as.character(chron(bkByTAN[[j]]$Requested.Ship.Date[i]))
              bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
              bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
              suppByTAN[[j]]$Quantity[closestDateIndex] <- suppByTAN[[j]]$Quantity[closestDateIndex] - bkByTAN[[j]]$Ordered.Quantity[i]
              bkByTAN[[j]]$Ordered.Quantity[i] <- 0
              #print('CRD<=LT, CRD > CBD, supply b4 CRD - TP')
            } else{
              print('else 1.2')
              #if there's not enough supply TP days before CRD - TP, then look for supplies after CRD but still before LTgoal - TP
              #first gotta update the closestDateIndex to the next bucket (after TP days before CRD)
              
              bkByTAN[[j]]$Ordered.Quantity[i] <- bkByTAN[[j]]$Ordered.Quantity[i] - suppByTAN[[j]]$Quantity[closestDateIndex]
              suppByTAN[[j]]$Quantity[closestDateIndex] <- 0
              closestDateIndex <- closestDateIndex + 1
            } #end of else
          } else if (suppByTAN[[j]]$Due.Date[closestDateIndex] <= (bkByTAN[[j]]$LTgoal[i] - TP)){
            print('else if 2')
          #if supply arived after CRD - TP, but still before LT; if CRD - TP < Due.Date <= LTgoal - TP
            if( suppByTAN[[j]]$Quantity[closestDateIndex] > bkByTAN[[j]]$Ordered.Quantity[i]){
              print('if 2.2')
              #if there is enough supply before LT - TP, then PD = Due.Date + TP
              bkByTAN[[j]]$newPD[i] <- as.character(suppByTAN[[j]]$Due.Date[closestDateIndex] + TP)
              bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
              bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
              suppByTAN[[j]]$Quantity[closestDateIndex] <- suppByTAN[[j]]$Quantity[closestDateIndex] - bkByTAN[[j]]$Ordered.Quantity[i]
              bkByTAN[[j]]$Ordered.Quantity[i] <- 0
              #print('CRD<=LT, CRD > CBD, supply b4 LT after CRD')
            } else {
              print('else 2.3')
              #if there's not enough supply before LT - TP, subtract and keep look forward up to LT - TP day
              bkByTAN[[j]]$Ordered.Quantity[i] <- bkByTAN[[j]]$Ordered.Quantity[i] - suppByTAN[[j]]$Quantity[closestDateIndex]
              suppByTAN[[j]]$Quantity[closestDateIndex] <- 0
              closestDateIndex <- closestDateIndex + 1
            } #end of else
          } else {
            print('else 3')
            #if no supply enough before LT - TP, meaning Due.Date > LT - TP, then we gotta put it on ITF + x
            bkByTAN[[j]]$newPD[i] <- as.character(bkByTAN[[j]]$LTgoal[i] + ATP.ITF.pad)
            bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) + 1), bkByTAN[[j]]$newPD[i])
            bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) + 1), bkByTAN[[j]]$newPD[i])
            break
            #print("no enough supply before LT - TP; put on ITF + x")
          } # end of else
        } # end of while
          
    } #end of else: if CRD <= LT & CRD > CBD + TP     
  } else {
    #if CRD > LT; set PD = CRD
      bkByTAN[[j]]$newPD[i] <- bkByTAN[[j]]$Requested.Ship.Date[i]
      bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
      bkByTAN[[j]]$newPD[i] <- ifelse(is.weekend(chron(bkByTAN[[j]]$newPD[i])), as.character(chron(bkByTAN[[j]]$newPD[i]) +1), bkByTAN[[j]]$newPD[i])
      #print('CRD > LT, PD = CRD')
  } # end of else 
    #print(paste('closest supply date = ', closestDate, ' closest date index = ', closestDateIndex))
    
  #now calculate for the new LAS
  bkByTAN[[j]]$newLAS[i] <- ifelse( bkByTAN[[j]]$CRDinLTflag[i] == 'Y', ifelse( chron(bkByTAN[[j]]$newPD[i]) <= bkByTAN[[j]]$LTgoal[i], 100, 0), ifelse( chron(bkByTAN[[j]]$newPD[i]) <= chron(bkByTAN[[j]]$Requested.Ship.Date[i]), 100, 0) )
  
  #also calculate the new OTS
  bkByTAN[[j]]$newOTS[i] <- ifelse( bkByTAN[[j]]$CRDinLTflag[i] == 'Y', ifelse( chron(bkByTAN[[j]]$Ship.Date[i]) <= bkByTAN[[j]]$LTgoal[i], 100, 0), ifelse( chron(bkByTAN[[j]]$Ship.Date[i]) <= chron(bkByTAN[[j]]$Requested.Ship.Date[i]), 100, 0) )
    
  } #end of 2nd (inner) for loop that iterates through all the request dates in each data.frame of the list
#     testsup2 <- suppByTAN[[1]]
#   testbk2 <- bkByTAN[[1]]
  
  #convert all Due.Date back to characters for readability
  suppByTAN[[j]]$Due.Date <- as.character(chron(suppByTAN[[j]]$Due.Date))
  
  ##write to a xlsx file (the results)
  write.xlsx(bkByTAN[[j]], file = "C:/Users/ali3/Documents/cisco/LAS project w Suman/ITF/analysis/newPD newLAS new OTS 5 TANs.xlsx", sheetName = paste("TAN", j, sep = ""), col.names = TRUE, row.names = FALSE, append = TRUE)
  #write.table(bkByTAN[[2]],file = paste(path, "newPD newLAS results2.csv", sep = ""), sep = ",")
  
} #end of 1st (outer) for loop that iterates through each TAN in the master TAN list
testbk1 <- bkByTAN[[1]]
testsup1 <- suppByTAN[[1]]
# testbk2 <- bkByTAN[[2]]
# testsup2 <- suppByTAN[[2]]
# testbk3 <- bkByTAN[[3]]
# testsup3 <- suppByTAN[[3]]
# testbk4 <- bkByTAN[[4]]
# testsup4 <- suppByTAN[[4]]


```



```{r}


```

create a table that stores all the results for all TAN's
```{r}
#create a result table (temporary like this)
#first put the TAN into the table
result <- data.table(1,2,3,4,5,6,7,8)
#then rename all the columns with following code
#names(result) <- c("PF", "TAN", "as-is LAS", "to-be LAS", 'change in LAS', 'as-is OTS', 'to-be OTS', 'change in OTS')
setnames(result, c("V1", "V2", "V3", "V4", "V5", "V6", "V7", "V8"), c("PF", "TAN", "as-is LAS", "to-be LAS", 'change in LAS', 'as-is OTS', 'to-be OTS', 'change in OTS'))

for(j in 1:length(TANvals)){
  #print(paste("j=", j, sep = ""))
  #calculate for the as is LAS
  temp1 <- table(bkByTAN[[j]]$LASnow)
  asisLAS <- ifelse(is.na(temp1['100']), 0, ifelse(is.na(temp1['0']), 100, (temp1['100'] / (temp1['0'] + temp1['100'])) * 100))
  
  #need to calculate for to be LAS.... shit
  temp2 <- table(bkByTAN[[j]]$newLAS)
  tobeLAS <- ifelse(is.na(temp2['100']), 0, ifelse(is.na(temp2['0']), 100, (temp2['100'] / (temp2['0'] + temp2['100'])) * 100))
  
  #claculate the diff btwn to be and as is: change = tobe - asis
  changeLAS <- tobeLAS - asisLAS
  
  #calculate as is OTS
  temp3 <- table(bkByTAN[[j]]$OTSnow)
  asisOTS <- ifelse(is.na(temp3['100']), 0, ifelse(is.na(temp3['0']), 100, (temp3['100'] / (temp3['0'] + temp3['100'])) * 100))
  
  #calculate to be OTS
  temp4 <- table(bkByTAN[[j]]$newOTS)
  tobeOTS <- ifelse(is.na(temp4['100']), 0, ifelse(is.na(temp4['0']), 100, (temp4['100'] / (temp4['0'] + temp4['100'])) * 100))
  
  #claculate the diff btwn to be and as is: change = tobe - asis
  changeOTS <- tobeOTS - asisOTS
  
  #combine all 3 values
  row2badd <- list(bkByTAN[[j]][bkByTAN[[j]]$TAN == TANvals[j], ]$Prod.Family[1], as.character(TANvals[j]), asisLAS, tobeLAS, changeLAS, asisOTS, tobeOTS, changeOTS)
  
  #finally modify the result table by row bind method
  result <- rbind(result, row2badd)
}

result <- result[-1, ]
row2badd <- list(" ", "average", mean(result$`as-is LAS`), mean(result$`to-be LAS`), mean(result$`change in LAS`), mean(result$`as-is OTS`), mean(result$`to-be OTS`), mean(result$`change in OTS`))
result <- rbind(result, row2badd)

##write the results table to the other TAN results sheets as well
  path <- "~/cisco/LAS project w Suman/ITF/analysis/individual TAN/"
  write.xlsx(result, file = "C:/Users/ali3/Documents/cisco/LAS project w Suman/ITF/analysis/newPD newLAS new OTS 5 TANs.xlsx", sheetName = "results table", col.names = TRUE, row.names = FALSE, append = TRUE)


```


```{r}


```


```{r}


```




